### 2016-10-06 supplement.tex
This fixes for me broken refs in pdf index
(to the "references" sections)
Apply grammar fixes suggested by @certik at #208

\flushbottom
\thispagestyle{empty}%
\vskip-36pt%
{\raggedright\sffamily\bfseries\fontsize{20}{25}\selectfont SymPy: Symbolic Computing in Python\par}%
\vskip10pt
{\raggedright\sffamily\fontsize{12}{16}\selectfont  Supplementary material\par}
\vskip25pt%

The supplementary material take a deeper look at certain topics in SymPy for
which there was not enough room to discuss in the paper.
Section~\ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections~\ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section~\ref{suppsec:numsimpl}
discusses numerical simplification.  Section~\ref{suppsec:examples} provides
additional examples for topics discussed in the main paper.  In section
\ref{suppsec:sympy-gamma} the SymPy Gamma
project is discussed.  Finally, section~\ref{suppsec:comp-mma}
has a
brief comparison of SymPy with Wolfram Mathematica.

@@

\bibliography{paper}

>>>>

\flushbottom
\thispagestyle{empty}%
\vskip-36pt%
{\raggedright\sffamily\bfseries\fontsize{20}{25}\selectfont SymPy: symbolic computing in Python\par}%
\vskip10pt
{\raggedright\sffamily\fontsize{12}{16}\selectfont  Supplementary material\par}
\vskip25pt%

The supplementary material takes a deeper look at certain topics in SymPy for
which there was not enough room to discuss in the paper.
Section~\ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections~\ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section~\ref{suppsec:numsimpl}
discusses numerical simplification.  Section~\ref{suppsec:examples} provides
additional examples for topics discussed in the main paper.  In section
\ref{suppsec:sympy-gamma} the SymPy Gamma
project is discussed.  Finally, section~\ref{suppsec:comp-mma}
has a
brief comparison of SymPy with Wolfram Mathematica.

@@

\phantomsection
\bibliography{paper}
